A quantum parallel Markov chain Monte Carlo

### 2021-11-30 main.tex
discussion first pass

>>>>

We have shown how parallel MCMC may enjoy quadratic speedups by combining quantum minimization with the Gumbel-max trick.  Within a QPMCMC iteration, the current state represents a warm start for the sampling-turned-optimization problem, leading to increased efficiencies for the quantum minimization algorithm.  This work leads to two immediate questions.  First, more recent quantum minimization algorithms exist \citep{baritompa2005grover,farhi2014quantum}.  Would these confer additional speedups for quantum parallel MCMC and benefit from warm-starting in a similar manner? Second, there are other algorithms in statistics and machine learning that require sampling from potentially costly discrete distributions \citep{liu2001theoretical,csillery2010approximate}.  Can we adapt  the proposed strategies to some of these?
